### 2012-04-02 latex/hardware.tex

En la figura \ref{fig:cuadricoptero} se puede apreciar una imagen de la plataforma utilizada.
\begin{figure}[H]
	\centering
	\includegraphics[width=0.5\textwidth]{./pics_eleccion_hardware/turboace.png}
	\caption{Turbo Ace X720}
	\label{fig:cuadricoptero}
\end{figure}

@@

\begin{figure} 
  \centering
  \subfloat[Mongoose]{\label{fig:mongoose}
  		\includegraphics[width=0.3\textwidth]
  			{./pics_eleccion_hardware/Mongoose.png}}
  \subfloat[Canmore GT-730F]{\label{fig:gps} 
  		\includegraphics[width=0.3\textwidth]
  			{./pics_eleccion_hardware/gps.jpg}}

>>>>

En la figura \ref{fig:cuadricoptero} se puede apreciar una imagen de la plataforma utilizada.
\begin{figure}[H]
	\centering
	\includegraphics[width=0.35\textwidth]{./pics_eleccion_hardware/turboace.png}
	\caption{Turbo Ace X720}
	\label{fig:cuadricoptero}
\end{figure}

@@

\begin{figure} 
  \centering
  \subfloat[Mongoose]{\label{fig:mongoose}
  		\includegraphics[width=0.15\textwidth]
  			{./pics_eleccion_hardware/Mongoose.png}}\hspace{2cm}
  \subfloat[Canmore GT-730F]{\label{fig:gps} 
  		\includegraphics[width=0.15\textwidth]
  			{./pics_eleccion_hardware/gps.jpg}}
